Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Workshop Using Cutting-Edge Tools

### 2021-01-09 paper_contents.tex
Add JooYoung's bio

>>>>

JooYoung Seo is a doctoral candidate in Learning, Design, and Technology program at Penn State, and RStudio-certified data science instructor. His research involves accessible computing and multi-modal data representation for learners with and without (dis)abilities. He was interning on both RStudio IDE and Shiny (interactive data interface) team at RStudio in summer 2020. He is a developer and maintainer of the islsdown (R Markdown) package.
